SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-06 method.tex
Modified to reflect SimPoint methodology

\noindent \textit{Multi-core performance:} For multi-application workloads, we generate
100 random mixes and another 100 mixes from the memory intensive subset of
SPEC CPU 2017. For 4-core workload, 200 Million instructions are used for warm-up
and additional 1 Billion instruction simulated for collecting statistics.
Each CPU keeps executing its workload till the last CPU completes one billion
instructions after warm-up. For collecting IPC and other data, only the first
billion instructions are considered as the region of interest.\\

@@

In total, we used 285 traces representing workloads across 53 applications.
Throughout the paper, we consider memory intensive subset as the
traces with LLC MPKI > 1. This includes 48 out of the 95 simpoints
developed for SPEC CPU 2017. For SPEC CPU 2006, this includes 48 out of 94 simpoints.

>>>>

\noindent \textit{Multi-core performance:} For multi-application workloads, we generate
100 random mixes and another 100 mixes from the memory intensive subset of
SPEC CPU 2017. For 4-core workload, 200 Million instructions are used for warm-up
and additional 1 Billion instruction simulated for collecting statistics.
Each CPU keeps executing its workload till the last CPU completes one billion
instructions after warm-up. For collecting IPC and other data, only the first
billion instructions are considered as the region of interest.

@@

In total, we used 285 traces representing workloads across 53 applications.
Throughout the paper, we consider memory intensive subset as the
applications with SimPoint weighted LLC MPKI > 1. This includes 11 out of 
20 SPEC CPU 2017 applications. For SPEC CPU 2006, this includes 16 out of 
29 applications.
